### 2015-04-20 paper.tex
Style fixes
Add facility and instrumentation section from test plan

\section*{Materials and Methods}
\subsection*{Turbine Model}

% For figure citations, please use "Fig." instead of "Figure".
A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Table~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Figure~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l}
   & Full-scale & Model (1:6) \\
\hline 
Diameter (m)   & 6.450 & 1.075 \\ 
Height (m)     & 4.840 & 0.8067 \\ 
Blade root chord (m) & 0.4000 & 0.06667 \\ 
Blade tip chord (m)  & 0.2400 & 0.04000 \\ 
Blade profile & NACA 0021 & NACA 0021 \\ 
Blade mount & 1/2 chord & 1/2 chord \\ 
Blade pitch (deg.) & 0.0 & 0.0 \\ 
Strut profile & NACA 0021 & NACA 0021 \\ 
Strut chord (m) & 0.3600 & 0.06000 \\ 
Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350\\ 
\end{tabular}
\caption{RM2 turbine geometric parameters.}
\label{tab:turb-geom}
\end{table}

@@

>>>>

\section*{Materials and Methods}

\subsection*{Turbine Model}

% For figure citations, please use "Fig." instead of "Figure".
A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l}
   & Full-scale & Model (1:6) \\
\hline 
Diameter (m)   & 6.450 & 1.075 \\ 
Height (m)     & 4.840 & 0.8067 \\ 
Blade root chord (m) & 0.4000 & 0.06667 \\ 
Blade tip chord (m)  & 0.2400 & 0.04000 \\ 
Blade profile & NACA 0021 & NACA 0021 \\ 
Blade mount & 1/2 chord & 1/2 chord \\ 
Blade pitch (deg.) & 0.0 & 0.0 \\ 
Strut profile & NACA 0021 & NACA 0021 \\ 
Strut chord (m) & 0.3600 & 0.06000 \\ 
Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350\\ 
\end{tabular}
\caption{\textbf{RM2 turbine geometric parameters.}}
\label{tab:turb-geom}
\end{table}

@@

\subsection*{Facility and instrumentation}

Experiments were performed in the UNH tow/wave tank, a 36 m long facility with a
3.66 m wide by 2.44 m deep cross-section, capable of tow speeds up to 3 m/s,
pictured in Figure~\ref{fig:tow-tank}. The turbine was mounted in a frame built
from NACA 0020 struts, attached to the tow carriage by four linear bearings,
which transfer all streamwise force to a pair of S-beam load cells. The turbine
shaft RPM was controlled by a servo motor system, which allowed prescription of
the turbine tip speed ratio. The load torque was measured by an inline rotary
torque transducer and a load cell mounted at a fixed distance from the servo
motor, providing a redundant measurement. Turbine shaft angle was measured using
the servo drive's emulated encoder output, set to $10^5$ counts per turbine
shaft revolution. Carriage speed, and therefore inflow velocity was measured
using a linear encoder with 10 $\mu$m resolution. All of these
performance-related quantities were sampled as 2 kHz, while the tow tank's
motion controller provided redundant measurements of the carriage speed and
turbine angular velocity sampled at 1 kHz. Turbine wake measurements at 1 meter
downstream were measured with a Nortek Vectrino+ acoustic Doppler velocimeter,
sampling at 200 Hz. A drawing of the experimental setup is shown in
Figure~\ref{fig:exp-setup}.

\begin{figure}[h]
\caption{Photos of the UNH towing tank and turbine test bed.} 
\label{fig:tow-tank}
\end{figure}

\begin{figure}[h]
\centering
%\includegraphics[clip,trim=0.01in 0 0 0,
%width=0.95\textwidth]{Figures/tank_cross_section}
\caption{Illustration of the experimental setup.}
\label{fig:exp-setup}
\end{figure}

\paragraph{Synchronization.} The three data acquisition instrumentation
subsystems---motion controller, NI DAQ (performance measurements), and Vectrino+
(wake velocity measurements)---started sampling at precisely the same time each
tow, after being triggered by a TTL pulse created by the motion controller. This
strategy retained synchronization for all performance signal samples (tow speed,
torque, drag, angular velocity), ensuring precise calculation of, e.g., power
coefficient. Since there is also synchronization of the initial sample from each
three subsystems, correlation of events in the performance and wake signals is
also possible.

\paragraph{Tare drag and torque compensation.} Tare torque and drag runs were
performed to measure the shaft bearing friction torque and turbine mounting
frame drag, respectively. Tare drag runs were performed for each tow speed in
the experiment, for which the mean value was used in data processing. Tare
torque runs were performed by rotating the turbine shaft (without blades) in air
at constant angular velocity for a specified duration, over the range of angular
velocities used throughout the experiment. Tare torque was fit with a linear
regression versus shaft angular velocity, and added to the measured turbine
torque in post-processing.
